Honeybees vary collective decision making in different landscapes. 

### 2022-07-26 analysis/manuscript/paper.Rmd
Updated refs for new version

---
title: "Waggle dance distributions quantify collective foraging in honey bee colonies"
# author: "Joseph Palmer, Ash Samuelson, Elli Leadbeater and Vincent A. A. Jansen"
output:
  word_document
always_allow_html: true
bibliography: paper-refs.bib
csl: science.csl
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(showtext)
showtext_auto()

@@

In group living animals, many decisions are taken collectively by integrating information from individuals to produce a social behaviour which extends beyond that of the individual units [@Sumpter2006]. Such systems are self-organised, relying on the constituents using socially provided information and following behavioural 'rules' to produce a collective outcome [@Couzin2003;@Bonabeau1997]. However, in addition to information provided by others, individuals also have knowledge of their own (private information) and so can choose to work collectively or individually [@Dall2005;@Reiucau2011;@Gruter2014]. The benefits of working collectively versus independently vary across environmental contexts and individuals often adjust their own use of information accordingly [@Dechaume-Moncharmont2005;@Beekman2008]. The impact these individual variations in information use have at a group level, however, is less well understood and difficult to empirically evaluate [@Rieucau2011;@Giardina2008;@Delgado2018].

@@

Social insects are defined by their highly coordinated collective responses and so provide ideal systems to investigate the impact of individual variation in information use on emergent collective processes. Nevertheless, the sheer quantity of individuals in many colonies is a barrier to further understanding these dynamics. Honey bees (Apis spp.) provide an opportunity to sidestep this problem of scale as they provide a detailed record of colony foraging activity in the form of their unique waggle dance -unparalleled in even a single other social insect [@Seeley1995]. Using the dance, individuals share information about profitable resource locations. A series of simple rules which determine when and how much bees perform waggle dances (Fig. 1) mean that choices between feeding sites occur at the level of the group rather than the individual [@Seeley1991;@Seeley2004;@Hasenjager2022]. Despite this, a wealth of research shows that individual foragers frequently do not use dance information to find forage sites and instead rely on their own knowledge [@Gruter2009]. Moreover, studies investigating the value of the dance have shown that when prevented from communicating via dances, honey bee colonies can achieve equal or even greater foraging success than their wild-type counterparts [@Sherman2002;@Dornhaus2004;@Gruter2013;@Price2019].

>>>>

---
title: "Honeybees vary collective decision making in different landscapes. "
# author: "Joseph Palmer, Ash Samuelson, Elli Leadbeater and Vincent A. A. Jansen"
output:
  word_document
always_allow_html: true
bibliography: reffs.bib
csl: science.csl
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(showtext)
showtext_auto()

@@

In group living animals, many decisions are taken collectively by integrating information from individuals to produce a social behaviour which extends beyond that of the individual units [@Sumpter2006]. Such systems are self-organised, relying on the constituents using socially provided information and following behavioural 'rules' to produce a collective outcome [@Couzin2003;@Bonabeau1997]. However, in addition to information provided by others, individuals also have knowledge of their own (private information) and so can choose to work collectively or individually [@Dall2005;@Rieucau2011;@Gruter2014]. The benefits of working collectively versus independently vary across environmental contexts and individuals often adjust their own use of information accordingly [@Dechaume-Moncharmont2005;@Beekman2008]. The impact these individual variations in information use have at a group level, however, is less well understood and difficult to empirically evaluate [@Rieucau2011;@Giardina2008;@Delgado2018].

@@

Social insects are defined by their highly coordinated collective responses and so provide ideal systems to investigate the impact of individual variation in information use on emergent collective processes. Nevertheless, the sheer quantity of individuals in many colonies is a barrier to further understanding these dynamics. Honey bees (Apis spp.) provide an opportunity to sidestep this problem of scale as they provide a detailed record of colony foraging activity in the form of their unique waggle dance -unparalleled in even a single other social insect [@Seeley1995]. Using the dance, individuals share information about profitable resource locations. A series of simple rules which determine when and how much bees perform waggle dances (Fig. 1) mean that choices between feeding sites occur at the level of the group rather than the individual [@Seeley1991;@Seeley1994A;@Hasenjager2022]. Despite this, a wealth of research shows that individual foragers frequently do not use dance information to find forage sites and instead rely on their own knowledge [@Gruter2009]. Moreover, studies investigating the value of the dance have shown that when prevented from communicating via dances, honey bee colonies can achieve equal or even greater foraging success than their wild-type counterparts [@Sherman2002;@Dornhaus2004;@Gruter2013;@Price2019].
